\documentclass{../../../fal_assignment}
\graphicspath{ {../../../} }

\usepackage{enumitem}
\setlist{nosep} % Make enumerate / itemize lists more closely spaced
\usepackage[T1]{fontenc} % http://tex.stackexchange.com/a/17858
\usepackage{url}
\usepackage{todonotes}

\title{Worksheet Tasks}
\author{Alcwyn Parker} 
\module{Intellectual Property }

\begin{document}

\maketitle

\begin{marginquote}
`Copying all or parts of a program is as natural to a programmer as breathing, and as productive. It ought to be as free.'
\par --- The GNU Manifesto
\end{marginquote}

\section*{Introduction}

There are a huge variety of different software licenses, from the sublime to the absurd. Some licenses are extremely strict and insure that software can not be copied or modified others declare the code as free and open for all to use. The difficulty is when code bases with different licenses collide. How do you consolidate the licenses, insure correct attribution and stay on the right side of the law? 

The goals of this workshop is to obtain a good working knowledge of the various software licenses and how and when they should be applied. Alongside this you will be expected to consider the implications of software licenses applied to existing code that you include in your own work. This will enable you to operate in a professional context with confidence and within the law, as well as give you the skills to take control of your own IP.
 

\section*{Objectives}
\begin{enumerate}[label=(\Alph*)]
	\item \textbf{Identify} the most popular software licenses 
	\item \textbf{Outline} the strengths and weaknesses of the various mainstream software licenses
	\item \textbf{Select} the most appropriate software license for your own IP
\end{enumerate}

\section*{Worksheet Setup}

In order to complete this worksheet you will be put into groups and asked to research one specific software license. 

\section*{Worksheet Tasks}
\begin{itemize}
	\item Familiarise yourself with the various software licenses
	\item Carry out in depth research into a specific software license:
		\begin{itemize}
			\item Who is attributed to developing the license?
			\item What are the key requirements of the license?
			\item What are the strengths and weaknesses of the license?
			\item Who is using the license in a professional context?
			\item Have there been any major legal battles involving the license and how were they resolved?
			\item What licenses might be considered the antithesis of the software license in question?
		\end{itemize}
		\item Select one member of the group to summarise the findings and report back to the rest of the cohort. 
\end{itemize}


\section*{Additional Guidance}

The goal of this worksheet is to get you up to speed with the various different software licenses very quickly. The reason that you are working in groups is so that you can share the load. This activity should not take you more the 30mins and the cumulative effort of the entire cohort should help to broaden each individuals understanding of software licenses. Wikipedia will undoubtedly be a very useful resource here, but try to go beyond this source and focus on getting to the origins of each license. 

\section*{Additional Resources}

\begin{itemize}
    \item Coding Horror \url{https://blog.codinghorror.com/pick-a-license-any-license/}
    \item Wikipedia \url{https://en.wikipedia.org/wiki/Software_license}
    \item Linda.com \url{https://www.lynda.com/Programming-Foundations-tutorials/What-software-license/439414/481240-4.html}
\end{itemize}

\end{document}
